Diversity, Segregation, and Complexity in Cities

### 2016-11-01 submission.tex
created outline with hipster ipsum

@@

% Use letters for affiliations, numbers to show equal authorship (if applicable) and to indicate the corresponding author
\author[a,c,1]{Author One}
\author[b,1,2]{Author Two} 
\author[a]{Author Three}

\affil[a]{Affiliation One}
\affil[b]{Affiliation Two}
\affil[c]{Affiliation Three}

% Please give the surname of the lead author for the running footer
\leadauthor{Lead author last name}

@@

% Please include corresponding author, author contribution and author declaration information
\authorcontributions{Please provide details of author contributions here.}
\authordeclaration{Please declare any conflict of interest here.}
\equalauthors{\textsuperscript{1}A.O.(Author One) and A.T. (Author Two) contributed equally to this work (remove if not applicable).}
\correspondingauthor{\textsuperscript{2}To whom correspondence should be addressed. E-mail: author.two\@email.com}

% Keywords are not mandatory, but authors are strongly encouraged to provide them. If provided, please include two to five keywords, separated by the pipe symbol, e.g:
\keywords{Keyword 1 $|$ Keyword 2 $|$ Keyword 3 $|$ ...}

@@

% If your first paragraph (i.e. with the \dropcap) contains a list environment (quote, quotation, theorem, definition, enumerate, itemize...), the line after the list may have some extra indentation. If this is the case, add \parshape=0 to the end of the list environment.
\dropcap{T}his PNAS journal template is provided to help you write your work in the correct journal format.  Instructions for use are provided below.

Note: please start your introduction without including the word ``Introduction'' as a section heading (except for math articles in the Physical Sciences section); this heading is implied in the first paragraphs.

\section*{Guide to using this template on Overleaf}

Please note that whilst this template provides a preview of the typeset manuscript for submission, to help in this preparation, it will not necessarily be the final publication layout. For more detailed information please see the \href{http://www.pnas.org/site/authors/format.xhtml}{PNAS Information for Authors}.

If you have a question while using this template on Overleaf, please use the help menu (``?'') on the top bar to search for \href{https://www.overleaf.com/help}{help and tutorials}. You can also \href{https://www.overleaf.com/contact}{contact the Overleaf support team} at any time with specific questions about your manuscript or feedback on the template.

\subsection*{Author Affiliations}

Include department, institution, and complete address, with the ZIP/postal code, for each author. Use lower case letters to match authors with institutions, as shown in the example. Authors with an ORCID ID may supply this information at submission.

\subsection*{Submitting Manuscripts}

All authors must submit their articles at \href{http://www.pnascentral.org/cgi-bin/main.plex}{PNAScentral}. If you are using Overleaf to write your article, you can use the ``Submit to PNAS'' option in the top bar of the editor window.

\subsection*{Format}

Many authors find it useful to organize their manuscripts with the following order of sections;  Title, Author Affiliation, Keywords, Abstract, Significance Statement, Results, Discussion, Materials and methods, Acknowledgments, and References. Other orders and headings are permitted.

\subsection*{Manuscript Length}

PNAS generally uses a two-column format averaging 67 characters, including spaces, per line. The maximum length of a Direct Submission research article is six pages and a PNAS PLUS research article is ten pages including all text, spaces, and the number of characters displaced by figures, tables, and equations.  When submitting tables, figures, and/or equations in addition to text, keep the text for your manuscript under 39,000 characters (including spaces) for Direct Submissions and 72,000 characters (including spaces) for PNAS PLUS.

\subsection*{References}

References should be cited in numerical order as they appear in text; this will be done automatically via bibtex, e.g. \cite{belkin2002using} and \cite{berard1994embedding,coifman2005geometric}. All references, including for the SI, should be included in the main manuscript file. References appearing in both sections should not be duplicated.  SI references included in tables should be included with the main reference section.

\subsection*{Data Archival}

PNAS must be able to archive the data essential to a published article. Where such archiving is not possible, deposition of data in public databases, such as GenBank, ArrayExpress, Protein Data Bank, Unidata, and others outlined in the Information for Authors, is acceptable.

\subsection*{Language-Editing Services}
Prior to submission, authors who believe their manuscripts would benefit from professional editing are encouraged to use a language-editing service (see list at www.pnas.org/site/authors/language-editing.xhtml). PNAS does not take responsibility for or endorse these services, and their use has no bearing on acceptance of a manuscript for publication.

\begin{figure}%[tbhp]
\centering
\includegraphics[width=.8\linewidth]{frog}
\caption{Placeholder image of a frog with a long example caption to show justification setting.}
\label{fig:frog}
\end{figure}

\begin{SCfigure*}[\sidecaptionrelwidth][t]
\centering
\includegraphics[width=11.4cm,height=11.4cm]{frog}
\caption{This caption would be placed at the side of the figure, rather than below it.}\label{fig:side}
\end{SCfigure*}

\subsection*{Digital Figures}
\label{sec:figures}

Only TIFF, EPS, and high-resolution PDF for Mac or PC are allowed for figures that will appear in the main text, and images must be final size. Authors may submit U3D or PRC files for 3D images; these must be accompanied by 2D representations in TIFF, EPS, or high-resolution PDF format.  Color images must be in RGB (red, green, blue) mode. Include the font files for any text.

Figures and Tables should be labelled and referenced in the standard way using the \verb|\label{}| and \verb|\ref{}| commands.

Figure \ref{fig:frog} shows an example of how to insert a column-wide figure. To insert a figure wider than one column, please use the \verb|\begin{figure*}...\end{figure*}| environment. Figures wider than one column should be sized to 11.4 cm or 17.8 cm wide. Use \verb|\begin{SCfigure*}...\end{SCfigure*}| for a wide figure with side captions.

\subsection*{Single column equations}

Authors may use 1- or 2-column equations in their article, according to their preference.

To allow an equation to span both columns, options are to use the \verb|\begin{figure*}...\end{figure*}| environment mentioned above for figures, or to use the \verb|\begin{widetext}...\end{widetext}| environment as shown in equation \ref{eqn:example} below.

Please note that this option may run into problems with floats and footnotes, as mentioned in the \href{http://texdoc.net/pkg/cuted}{cuted package documentation}. In the case of problems with footnotes, it may be possible to correct the situation using commands \verb|\footnotemark| and \verb|\footnotetext|.

%% Do not use widetext if paper is in single column.
\begin{widetext}
\begin{align*}
(x+y)^3&=(x+y)(x+y)^2\\
       &=(x+y)(x^2+2xy+y^2) \numberthis \label{eqn:example} \\
       &=x^3+3x^2y+3xy^3+x^3. 
\end{align*}
\end{widetext}

\begin{table}%[tbhp]
\centering
\caption{Comparison of the fitted potential energy surfaces and ab initio benchmark electronic energy calculations}
\begin{tabular}{lrrr}
Species & CBS & CV & G3 \\
\midrule
1. Acetaldehyde & 0.0 & 0.0 & 0.0 \\
2. Vinyl alcohol & 9.1 & 9.6 & 13.5 \\
3. Hydroxyethylidene & 50.8 & 51.2 & 54.0\\
\bottomrule
\end{tabular}

\addtabletext{nomenclature for the TSs refers to the numbered species in the table.}
\end{table}

\subsection*{Supporting Information (SI)}

The main text of the paper must stand on its own without the SI. Refer to SI in the manuscript at an appropriate point in the text. Number supporting figures and tables starting with S1, S2, etc. Authors are limited to no more than 10 SI files, not including movie files. Authors who place detailed materials and methods in SI must provide sufficient detail in the main text methods to enable a reader to follow the logic of the procedures and results and also must reference the online methods. If a paper is fundamentally a study of a new method or technique, then the methods must be described completely in the main text. Because PNAS edits SI and composes it into a single PDF, authors must provide the following file formats only.

\subsubsection*{SI Text}

Supply Word, RTF, or LaTeX files (LaTeX files must be accompanied by a PDF with the same file name for visual reference).

\subsubsection*{SI Figures}

Provide a brief legend for each supporting figure after the supporting text. Provide figure images in TIFF, EPS, high-resolution PDF, JPEG, or GIF format; figures may not be embedded in manuscript text. When saving TIFF files, use only LZW compression; do not use JPEG compression. Do not save figure numbers, legends, or author names as part of the image. Composite figures must be pre-assembled.

\subsubsection*{3D Figures}

Supply a composable U3D or PRC file so that it may be edited and composed. Authors may submit a PDF file but please note it will be published in raw format and will not be edited or composed.

\subsubsection*{SI Tables}

Supply Word, RTF, or LaTeX files (LaTeX files must be accompanied by a PDF with the same file name for visual reference); include only one table per file. Do not use tabs or spaces to separate columns in Word tables.

\subsubsection*{SI Datasets}

Supply Excel (.xls), RTF, or PDF files. This file type will be published in raw format and will not be edited or composed.

\subsubsection*{SI Movies}

Supply Audio Video Interleave (avi), Quicktime (mov), Windows Media (wmv), animated GIF (gif), or MPEG files and submit a brief legend for each movie in a Word or RTF file. All movies should be submitted at the desired reproduction size and length. Movies should be no more than 10 MB in size.

\subsubsection*{Still images}

Authors must provide a still image from each video file. Supply TIFF, EPS, high-resolution PDF, JPEG, or GIF files.

\subsubsection*{Appendices}

PNAS prefers that authors submit individual source files to ensure readability. If this is not possible, supply a single PDF file that contains all of the SI associated with the paper. This file type will be published in raw format and will not be edited or composed.

@@

\acknow{Please include your acknowledgments here, set in a single paragraph. Please do not include any acknowledgments in the Supporting Information, or anywhere else in the manuscript.}

@@

% \pnasbreak splits and balances the columns before the references.
% Uncomment \pnasbreak to view the references in the PNAS-style
% If you see unexpected formatting errors, try commenting out \pnasbreak
% as it can run into problems with floats and footnotes on the final page.
%\pnasbreak

>>>>

%!TEX program = xelatex

@@

% Use letters for affiliations, numbers to show equal authorship (if applicable) and to indicate the corresponding author
\author[a,b,1]{Philip Chodrow}

\affil[a]{MIT Human Mobility and Networks Laboratory}
\affil[b]{MIT Operations Research Center}

% Please give the surname of the lead author for the running footer
\leadauthor{Chodrow}

@@

% Please include corresponding author, author contribution and author declaration information
% \authorcontributions{Please provide details of author contributions here.}
\authordeclaration{The author declares no competing interest.}
% \equalauthors{\textsuperscript{1}A.O.(Author One) and A.T. (Author Two) contributed equally to this work (remove if not applicable).}
\correspondingauthor{\textsuperscript{1}To whom correspondence should be addressed. E-mail: pchodrow@gmail.com}

% Keywords are not mandatory, but authors are strongly encouraged to provide them. If provided, please include two to five keywords, separated by the pipe symbol, e.g:
\keywords{Information Theory $|$ Diversity and Segregation $|$ Urban Theory $|$ ...}

@@

% If your first paragraph (i.e. with the \dropcap) contains a list environment (quote, quotation, theorem, definition, enumerate, itemize...), the line after the list may have some extra indentation. If this is the case, add \parshape=0 to the end of the list environment.
\dropcap{I}nformation theory...blah blah blah.

\section*{Results}

Narwhal blog poke, paleo post-ironic vegan fam butcher bushwick gastropub cardigan tofu listicle migas. Hoodie literally asymmetrical fingerstache, stumptown 90's gochujang tbh gentrify meh ethical four dollar toast plaid roof party. Bicycle rights kinfolk man braid disrupt XOXO. Leggings blue bottle post-ironic enamel pin tacos, hexagon brunch. Celiac 3 wolf moon kitsch tote bag bespoke pop-up. Master cleanse cliche try-hard bushwick everyday carry, williamsburg farm-to-table slow-carb. Paleo you probably haven't heard of them whatever typewriter normcore.

Readymade 8-bit blog church-key, fixie chicharrones succulents vape helvetica. Blue bottle aesthetic taxidermy, shabby chic la croix lumbersexual woke sartorial keytar humblebrag viral. Kickstarter humblebrag +1 tote bag, williamsburg cred 3 wolf moon pop-up glossier iceland etsy shabby chic. Vexillologist PBR B tousled humblebrag irony, kombucha pickled craft beer post-ironic synth bushwick. Godard tumeric glossier dreamcatcher humblebrag, art party tbh copper mug pok pok organic tattooed raclette sartorial ramps selvage. Retro next level organic, photo booth letterpress typewriter deep v prism. Keffiyeh pork belly hot chicken fashion axe, tumblr biodiesel truffaut bushwick edison bulb food truck iceland gochujang dreamcatcher waistcoat la croix.

Fanny pack poutine trust fund cardigan. Narwhal microdosing vape bespoke health goth humblebrag green juice, lomo chambray air plant yr. Pickled gastropub vegan etsy. Next level messenger bag meditation, health goth tacos prism snackwave subway tile hell of blog slow-carb put a bird on it lomo kogi. Roof party fixie pok pok, cardigan prism next level woke lomo. Venmo butcher irony, single-origin coffee gastropub cliche tumblr. Fap pour-over banjo, freegan literally direct trade etsy.

Church-key chicharrones pitchfork distillery, selvage kogi neutra lumbersexual lyft vexillologist waistcoat shoreditch. Kombucha whatever pug microdosing pitchfork. Activated charcoal ethical affogato echo park. Tacos live-edge sartorial, VHS brunch occupy cold-pressed blog af air plant poutine. Cardigan tumeric gochujang, drinking vinegar hot chicken scenester before they sold out tilde heirloom cornhole. Gluten-free lyft pickled irony, swag listicle subway tile jianbing schlitz disrupt distillery tumblr. Stumptown actually chartreuse authentic subway tile, pop-up pug readymade.

\subsection*{Using some damn math} 
There's lots of damn math we could use.

\section*{Discussion}

Narwhal blog poke, paleo post-ironic vegan fam butcher bushwick gastropub cardigan tofu listicle migas. Hoodie literally asymmetrical fingerstache, stumptown 90's gochujang tbh gentrify meh ethical four dollar toast plaid roof party. Bicycle rights kinfolk man braid disrupt XOXO. Leggings blue bottle post-ironic enamel pin tacos, hexagon brunch. Celiac 3 wolf moon kitsch tote bag bespoke pop-up. Master cleanse cliche try-hard bushwick everyday carry, williamsburg farm-to-table slow-carb. Paleo you probably haven't heard of them whatever typewriter normcore.

Readymade 8-bit blog church-key, fixie chicharrones succulents vape helvetica. Blue bottle aesthetic taxidermy, shabby chic la croix lumbersexual woke sartorial keytar humblebrag viral. Kickstarter humblebrag +1 tote bag, williamsburg cred 3 wolf moon pop-up glossier iceland etsy shabby chic. Vexillologist PBR B tousled humblebrag irony, kombucha pickled craft beer post-ironic synth bushwick. Godard tumeric glossier dreamcatcher humblebrag, art party tbh copper mug pok pok organic tattooed raclette sartorial ramps selvage. Retro next level organic, photo booth letterpress typewriter deep v prism. Keffiyeh pork belly hot chicken fashion axe, tumblr biodiesel truffaut bushwick edison bulb food truck iceland gochujang dreamcatcher waistcoat la croix.

Fanny pack poutine trust fund cardigan. Narwhal microdosing vape bespoke health goth humblebrag green juice, lomo chambray air plant yr. Pickled gastropub vegan etsy. Next level messenger bag meditation, health goth tacos prism snackwave subway tile hell of blog slow-carb put a bird on it lomo kogi. Roof party fixie pok pok, cardigan prism next level woke lomo. Venmo butcher irony, single-origin coffee gastropub cliche tumblr. Fap pour-over banjo, freegan literally direct trade etsy.

Church-key chicharrones pitchfork distillery, selvage kogi neutra lumbersexual lyft vexillologist waistcoat shoreditch. Kombucha whatever pug microdosing pitchfork. Activated charcoal ethical affogato echo park. Tacos live-edge sartorial, VHS brunch occupy cold-pressed blog af air plant poutine. Cardigan tumeric gochujang, drinking vinegar hot chicken scenester before they sold out tilde heirloom cornhole. Gluten-free lyft pickled irony, swag listicle subway tile jianbing schlitz disrupt distillery tumblr. Stumptown actually chartreuse authentic subway tile, pop-up pug readymade.

Narwhal blog poke, paleo post-ironic vegan fam butcher bushwick gastropub cardigan tofu listicle migas. Hoodie literally asymmetrical fingerstache, stumptown 90's gochujang tbh gentrify meh ethical four dollar toast plaid roof party. Bicycle rights kinfolk man braid disrupt XOXO. Leggings blue bottle post-ironic enamel pin tacos, hexagon brunch. Celiac 3 wolf moon kitsch tote bag bespoke pop-up. Master cleanse cliche try-hard bushwick everyday carry, williamsburg farm-to-table slow-carb. Paleo you probably haven't heard of them whatever typewriter normcore.

Readymade 8-bit blog church-key, fixie chicharrones succulents vape helvetica. Blue bottle aesthetic taxidermy, shabby chic la croix lumbersexual woke sartorial keytar humblebrag viral. Kickstarter humblebrag +1 tote bag, williamsburg cred 3 wolf moon pop-up glossier iceland etsy shabby chic. Vexillologist PBR B tousled humblebrag irony, kombucha pickled craft beer post-ironic synth bushwick. Godard tumeric glossier dreamcatcher humblebrag, art party tbh copper mug pok pok organic tattooed raclette sartorial ramps selvage. Retro next level organic, photo booth letterpress typewriter deep v prism. Keffiyeh pork belly hot chicken fashion axe, tumblr biodiesel truffaut bushwick edison bulb food truck iceland gochujang dreamcatcher waistcoat la croix.

Fanny pack poutine trust fund cardigan. Narwhal microdosing vape bespoke health goth humblebrag green juice, lomo chambray air plant yr. Pickled gastropub vegan etsy. Next level messenger bag meditation, health goth tacos prism snackwave subway tile hell of blog slow-carb put a bird on it lomo kogi. Roof party fixie pok pok, cardigan prism next level woke lomo. Venmo butcher irony, single-origin coffee gastropub cliche tumblr. Fap pour-over banjo, freegan literally direct trade etsy.

Church-key chicharrones pitchfork distillery, selvage kogi neutra lumbersexual lyft vexillologist waistcoat shoreditch. Kombucha whatever pug microdosing pitchfork. Activated charcoal ethical affogato echo park. Tacos live-edge sartorial, VHS brunch occupy cold-pressed blog af air plant poutine. Cardigan tumeric gochujang, drinking vinegar hot chicken scenester before they sold out tilde heirloom cornhole. Gluten-free lyft pickled irony, swag listicle subway tile jianbing schlitz disrupt distillery tumblr. Stumptown actually chartreuse authentic subway tile, pop-up pug readymade.

% \subsubsection*{Different table}

% Supply Word, RTF, or LaTeX files (LaTeX files must be accompanied by a PDF with the same file name for visual reference); include only one table per file. Do not use tabs or spaces to separate columns in Word tables.

% \subsubsection*{Different table}

% Supply Word, RTF, or LaTeX files (LaTeX files must be accompanied by a PDF with the same file name for visual reference); include only one table per file. Do not use tabs or spaces to separate columns in Word tables.

% \subsubsection*{SI Datasets}

% Supply Excel (.xls), RTF, or PDF files. This file type will be published in raw format and will not be edited or composed.

% \subsubsection*{SI Movies}

% Supply Audio Video Interleave (avi), Quicktime (mov), Windows Media (wmv), animated GIF (gif), or MPEG files and submit a brief legend for each movie in a Word or RTF file. All movies should be submitted at the desired reproduction size and length. Movies should be no more than 10 MB in size.

% \subsubsection{Still images}

% Authors must provide a still image from each video file. Supply TIFF, EPS, high-resolution PDF, JPEG, or GIF files.

% \subsubsection*{Appendices}

% PNAS prefers that authors submit individual source files to ensure readability. If this is not possible, supply a single PDF file that contains all of the SI associated with the paper. This file type will be published in raw format and will not be edited or composed.

@@

\acknow{P.C. is grateful to Marta C. Gonz\'{a}lez for helpful discussion, and to MIT-Saudi Arabia...}

@@

% \pnasbreak splits and balances the columns before the references.
% Uncomment \pnasbreak to view the references in the PNAS-style
% If you see unexpected formatting errors, try commenting out \pnasbreak
% as it can run into problems with floats and footnotes on the final page.
% \pnasbreak
